\chapter*{Bibliografie} 
\addcontentsline{toc}{chapter}{Bibliografie}

\begin{itemize}
    \item Kenneth O. Stanley, Risto Miikkulainen. \textbf{Evolving Neural Networks through Augmenting Topologies}, \url{http://nn.cs.utexas.edu/downloads/papers/stanley.ec02.pdf}
    \item Michał Joachimczak, Reiji Suzuki,  Takaya Arita. \textbf{Fine grained artificial development for body-controller coevolution of soft-bodiedanimats}, \url{https://www.mitpressjournals.org/doi/pdf/10.1162/978-0-262-32621-6-ch040}
    \item Thomas Geijtenbeek, Michiel van de Panne, A. Frank van der Stappen. \textbf{Flexible Muscle-Based Locomotion for Bipedal Creatures} \url {https://www.cs.ubc.ca/~van/papers/2013-TOG-MuscleBasedBipeds/2013-TOG-MuscleBasedBipeds.pdf}
    \item Rafael Matsunaga. \textbf{Genetic Walkers}, \url{https://rednuht.org/genetic_walkers/}
    \item \textbf{Evolved Antenna} \url{https://en.wikipedia.org/wiki/Evolved_antenna}
    \item Gregory S.Hornby and Al Globus, Derek S. Linden, Jason D. Lohn. \textbf{Automated Antenna Design with Evolutionary Algorithms} \url{https://ti.arc.nasa.gov/m/pub-archive/1244h/1244%20(Hornby).pdf}
    \item Martin Foot. \textbf{Math-Library-Test}, \url{https://github.com/mfoo/Math-Library-Test}
    \item Glenn Fiedler. \textbf{Integration Basics} \url{https://web.archive.org/web/20190405191806/https://gafferongames.com/post/integration_basics/}
    \item Glenn Fiedler. \textbf{Physics in 3D} \url{https://web.archive.org/web/20181107181511/https://gafferongames.com/post/physics_in_3d/}
    \item Glenn Fiedler. \textbf{Fix Your Timestep!} \url{https://web.archive.org/web/20190403012130/https://gafferongames.com/post/fix_your_timestep/}
\end{itemize} 